---
title: "Predictive Model Analysis"
author: "Corinne Helman"
date: "April 8, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#install necessary packages to load necessary libraries into RStudio

install.packages("tm")
install.packages("ngram")
install.packages("knitr")
install.packages("dplyr")
install.packages("ggplot2")
install.packages("RWeka")
install.packages("SnowballC")
install.packages("plyr")


library(tm)
library(ngram)
library(plyr)
library(knitr)
library(dplyr)
library(ggplot2)
library(RWeka)
library(SnowballC)


```{r}
setwd("/Users/Corinne/Desktop/Save 10 janvier 2018/Coursera/Capstone")
```

```{r,echo=TRUE}
news <- readLines(con <- file("./en_US.news.txt"), encoding = "UTF-8", skipNul = TRUE)
close(con)

set.seed(123)
linestoread <- 1500
train.news <- sample(news, linestoread, replace=FALSE)

banned <- readLines(con <- file("./badwords.txt"), encoding = "UTF-8", skipNul = TRUE)
close(con)
```
f <- content_transformer(function(x, pattern) gsub(pattern, "", x))

vecsource <- VectorSource(train.news)
corpus <- VCorpus(vecsource)
corpus <- tm_map(corpus, f, "[!\"#$%&'*+,./)(:;<=>?@][\\^`{|}~]")
corpus <- tm_map(corpus, f, "(f|ht)tp(s?)://(.*)[.][a-z]+")
corpus <- tm_map(corpus, f, "@[^\\s]+")
corpus <- tm_map(corpus, tolower)
corpus <- tm_map(corpus, removeWords, stopwords("en"))
corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, removeNumbers)
corpus <- tm_map(corpus, removeWords, banned) 
corpus <- tm_map(corpus, stripWhitespace)
corpus <- tm_map(corpus, PlainTextDocument)
```



```{r, echo=TRUE}

tdm_Ngram <- function (textcp, n) {
  NgramTokenizer <- function(x) {RWeka::NGramTokenizer(x, RWeka::Weka_control(min = n, max = n))}
  tdm_ngram <- TermDocumentMatrix(textcp, control = list(tokenizer = NgramTokenizer))
  tdm_ngram
}

ngram_sorted_df <- function (tdm_ngram) {
  tdm_ngram_m <- as.matrix(tdm_ngram)
  tdm_ngram_df <- as.data.frame(tdm_ngram_m)
  colnames(tdm_ngram_df) <- "Count"
  tdm_ngram_df <- tdm_ngram_df[order(-tdm_ngram_df$Count), , drop = FALSE]
  tdm_ngram_df
}

# Calculate N-Grams
tdm_1gram <- tdm_Ngram(corpus, 1)
tdm_2gram <- tdm_Ngram(corpus, 2)
tdm_3gram <- tdm_Ngram(corpus, 3)
tdm_4gram <- tdm_Ngram(corpus, 4)


# Extract term-count tables from N-Grams and sort 
tdm_1gram_df <- ngram_sorted_df(tdm_1gram)
tdm_2gram_df <- ngram_sorted_df(tdm_2gram)
tdm_3gram_df <- ngram_sorted_df(tdm_3gram)
tdm_4gram_df <- ngram_sorted_df(tdm_4gram)

# Save data frames into r-compressed files

quadgram <- data.frame(rows=rownames(tdm_4gram_df),count=tdm_4gram_df$Count)
quadgram$rows <- as.character(quadgram$rows)
quadgram_split <- strsplit(as.character(quadgram$rows),split=" ")
quadgram <- transform(quadgram,first = sapply(quadgram_split,"[[",1),second = sapply(quadgram_split,"[[",2),third = sapply(quadgram_split,"[[",3), fourth = sapply(quadgram_split,"[[",4))

quadgram <- data.frame(unigram = quadgram$first,bigram = quadgram$second, trigram = quadgram$third, quadgram = quadgram$fourth, freq = quadgram$count,stringsAsFactors=FALSE)


saveRDS(quadgram,"./NextWordPrediction/quadgram.RData")

trigram <- data.frame(rows=rownames(tdm_3gram_df),count=tdm_3gram_df$Count)
trigram$rows <- as.character(trigram$rows)
trigram_split <- strsplit(as.character(trigram$rows),split=" ")
trigram <- transform(trigram,first = sapply(trigram_split,"[[",1),second = sapply(trigram_split,"[[",2),third = sapply(trigram_split,"[[",3))

trigram <- data.frame(unigram = trigram$first,bigram = trigram$second, trigram = trigram$third, freq = trigram$count,stringsAsFactors=FALSE)

saveRDS(trigram,"./NextWordPrediction/trigram.RData")


bigram <- data.frame(rows=rownames(tdm_2gram_df),count=tdm_2gram_df$Count)
bigram$rows <- as.character(bigram$rows)
bigram_split <- strsplit(as.character(bigram$rows),split=" ")
bigram <- transform(bigram,first = sapply(bigram_split,"[[",1),second = sapply(bigram_split,"[[",2))

bigram <- data.frame(unigram = bigram$first,bigram = bigram$second,freq = bigram$count,stringsAsFactors=FALSE)

saveRDS(bigram,"./NextwordPrediction/bigram.RData")








